pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-07 manuscript/greenwell.tex
tweak abstract

\abstract{
Complex nonparametric models---like neural networks, random forests, and support vector machines---are more common than ever in predictive analytics, especially when dealing with large observational databases that don't adhere to the strict assumptions imposed by traditional statistical techniques (e.g., multiple linear regression). Unfortunately, it can be challenging for the uninitiated to understand the results of such models and explain them to management. Partial dependence plots offer a simple solution. Partial dependence plots are low-dimensional graphical renderings of the prediction function $\widehat{f}\left(\boldsymbol{x}\right)$ so that the relationship between the outcome and predictors of interest can be easily understood. These plots are especially useful in explaining the output from black box models or constructing simpler parsimonious models on newly obtained data. In this paper, we introduce \pkg{partial}, a general R package for constructing partial dependence plots
}

>>>>

\abstract{
Complex nonparametric models---like neural networks, random forests, and support vector machines---are more common than ever in predictive analytics, especially when dealing with large observational databases that don't adhere to the strict assumptions imposed by traditional statistical techniques (e.g., multiple linear regression). Unfortunately, it can be challenging for the uninitiated to understand the results of such models and explain them to management. Partial dependence plots offer a simple solution. Partial dependence plots are low-dimensional graphical renderings of the prediction function $\widehat{f}\left(\boldsymbol{x}\right)$ so that the relationship between the outcome and predictors of interest can be easily understood. These plots are especially useful in explaining the output from black box models. In this paper, we introduce \pkg{pdp}, a general R package for constructing partial dependence plots.
}
